---
title: "Trading with GARCH Forecast"
output: html_notebook
---



Read the Data
Import the file options_daily_sp500_2018_2022.csv using the read_csv method of pandas. It has the details of all monthly expiry options contracts available for the S&P 500 index from 2018 till 2022. For SPX options, the expiry date of monthly contract is the last trading day of the month.
The data includes the strike price of the options contract, the implied volatility and the price of calls, puts of the strike price.

This CSV file is available in the zip file of the unit 'Python Codes and Data' in the 'Course Summary' section.

```{r}
library(tidyverse)
# Read the data
options_data = read_csv("../../Quantra/data_modules/options_daily_sp500_2018_2022.csv")

# Change the index type to datetime
options_data <- rename(options_data, Date=`...1`) %>% mutate(Date=as.Date(Date))

# Import the S&P 500 index daily data
daily_data_SP500 = read_csv("../../Quantra/data_modules/daily_sp500_2018_2022.csv")

# Merge both dataframes to include the information of underlying data into options data
options_data <- merge(options_data, daily_data_SP500, by="Date")

# Display the data
options_data %>% tail
```
Generate the Trading Signals
For every day in the last one year of data in options_data, perform the following steps to generate trading signals.

Step-1: Select the 4 years of daily options data before the selected date
Step-2: Resample the daily data into monthly data
Step-3: Estimate the monthly volatility using Parkinson volatility estimator
Step-4: Considering the estimated volatility as the input, estimate the parameters of the GARCH(1,1) model
Step-5: Forecast the volatility for the next month with GARCH(1,1) model with estimated parameters.
Step-6: If the forecasted volatility is greater than the implied volatility of ATM call and put options, buy a straddle. On the other hand, if the forecasted volatility is less than the implied volatility of ATM call and put options, sell a straddle.
Step-7: Once a long or short position is opened, close it after a week.
Step-8: Once the position is closed, re-estimate the model using the rolling 4 years of data, forecast volatility again for one month and generate the trading signals.
Before implementing the above steps, create the signal column in the options_data dataframe to store the trading signals.

signal = 1 if a long straddle position is to be opened.
signal = -1 if a short straddle position is to be opened.
signal = 0 if a long or short straddle position is to be closed.
Also, define the initial parameter values and their bounds for estimation of GARCH (1,1) parameters.

```{r}
# Create `signal_iv` column in the options_data dataframe
options_data['signal'] = 0

# Define the initial parameter values gamma, alpha, beta
initial_parameters = c(0.1, 0.1, 0.1)

# Bounds for gamma, alpha, beta
parameter_bounds = list(c(0, 1), c(0, 1), c(0, 1))
```

Since the trading signals are to be generated for the last one year of the options data, select the last one year of data from options_data and store it in data_last_one_year.
Since the trade should be held for one week, you need not check for trading signals every single day. So, create a counter days_since_last_signal to keep track of the number of days since the last trading signal.
Once the counter reaches 5, conditions to generate trade signals will be checked. This ensures that the trading signals are generated a week apart and no trading signal is generated when a position is open.
Initiate the counter with 5.
Reset the counter to 0 once a position is opened.

```{r}
# Select the last one year of data from options_data
last_one_year = options_data %>% tail(252*4)

# Initiate the counter with five
days_since_last_signal = 5
```


```{r}
options_data_monthly <-  group_by(options_data, M) %>% mutate(Days=n()-(1:n())+1, IV=C_IV*sqrt(Days)); options_data_monthly$RV=runSD(log(options_data_monthly$Close/lag(options_data_monthly$Close)), 20)*sqrt(252)

options_data_monthly <-  group_by(options_data, M) %>% reframe(M_High=max(High), M_Low=min(Low), M_HL=log(M_High/M_Low), M_Close=last(Close))
options_data_pk <- merge(options_data, options_data_monthly, by="M", all=T) %>% mutate(IV=C_IV*sqrt(Days))

# )
```

